---
title: "Teaching Activities at the UEB"
description: "Welcome to the Statistics and Bioinformatics Unit Teaching Activities web site. This page links with the web pages of different courses we are teaching right now or have taught in the past. In these pages you will find all the materials we use for the courses -unless of course they are copyrighted or under some type of confidentiality."
# author: "UEB@VHIR"
date: "`r Sys.Date()`"
output_dir: "docs"
output:
  distill::distill_article:
    toc: false
    toc_depth: 2
    fig_width: 8
    fig_height: 5
    # highlight: "textmate"
    theme: "default"
    self_contained: true
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
# Cargar librerías necesarias
library(htmltools)
```

<style> 
.highlight-box { background-color: #f8f9fa; border-left: 5px solid #ffc107; padding: 20px; margin: 20px 0; text-align: center; font-size: 1.5em; font-weight: bold; } 
.highlight-box ul { text-align: center; font-size: 0.9em; font-weight: normal; margin-top: 10px; list-style-type: none; padding-left: 0; } 
.column { width: 100%;   text-align: center;}
.center-title { text-align: center; margin: 40px 0 20px 0; font-size: 1.8em; font-weight: bold; }  
</style>

<div class="highlight-box"> Current Activity <ul> 
[2025-03: Sessió Bases de dades en REDCAP per infermeria](https://github.com/uebvhir/seminars/raw/master/Bases_de_dades_Infermeria_v2.pdf)
</ul> 
 

</div><div class="column">

### Past Courses 

**2023** 

 [Bioinformatics course for Biomedical Research. VHIR ](https://uebvhir.github.io/Course_Bioinformatics_2023.html) 

 [Basic Course of Data Analysis with STATA. PSPV ](https://uebvhir.github.io/Course_Basic_data_analysis_STATA_PV_2023.html) 
 
 [Basic Statistics for Biomedical Research. PreDocs VHIR ](https://uebvhir.github.io/Course_Basic_Statistics_VHIR_2023.html)

**2022** 

 [Basic Statistics for Biomedical Research. VHIR ](https://uebvhir.github.io/Course_Basic_Statistics_VHIR_2022.html) 
 
 [Bioinformatics course for Biomedical Research. VHIR ](https://uebvhir.github.io/Course_Bioinformatics_2022.html) 

**2021** 

 [Bioinformatics course for Biomedical Research. VHIR ](https://uebvhir.github.io/Course_Bioinformatics_2021.html) 
 
 [Basic Statistics for Biomedical Research. CSAPG 2021](https://uebvhir.github.io/Course_StatisticsR_2021-Garraf.html)
 
 [Basic Statistics for Biomedical Research. VHIO](https://uebvhir.github.io/Course_StatisticsR_2021-VHIO.html)
 
 [Basic Statistics for Biomedical Research. VHIR](https://uebvhir.github.io/Course_Basic_Statistics_VHIR_2021.html)
 

**2019-2020**

 [Curso de Estadística Básica con R (PV)](https://uebvhir.github.io/Course_Basic_Statistics_VHIR_2021.html)
  
 [Basic Statistics for Biomedical Research - VHIO](https://uebvhir.github.io/Course_StatisticsR_2020-VHIO.html)
  
 [Curs de Bioinformàtica per a la Recerca Biomèdica](https://uebvhir.github.io/Course_Bioinformatics_2020.html)
  
 [Basic Statistics for Biomedical Research - VHIO](https://uebvhir.github.io/Course_BasicStatistics_2019-VHIO.html)
  
 [Basic Statistics for Biomedical Research](https://cdn.staticaly.com/gh/uebvhir/Course_Basic_Statistics_2019/master/Desc_BasicStatistics_2019.html)
  
 [Sessió formativa Servei Otorrino](https://cdn.staticaly.com/gh/uebvhir/Sessions-Formatives/master/20190524_Sessio_Otorrino_estbasica.pdf)
  
 [Bioinformatics for clinical and biomedical research](https://uebvhir.github.io/bioinformatica2018.html)
  
 [Data Management, Programming and Graphics with R](https://uebvhir.github.io/R-Course.html)
  
  
  

### Past Pindoles 



**2022** 

  [29/04/2022: Propensity Score](https://github.com/uebvhir/Pindoles/raw/master/2022-04-29_Pindola_propensity_score.pdf) 

  [25/02/2022: Introducció a l'Estadística Bayesiana](https://github.com/uebvhir/Pindoles/raw/master/2022-02-25_Pindola_Bayesian_Statistics.pdf) 

**2020** 

  [01/2020: Visualització moderna de dades](https://github.com/uebvhir/pindoles/raw/master/2020_01-Statistical_pill-Data_visualization.pdf) 
  
  [16/12/2019: Ajustos per multiple testing](https://github.com/uebvhir/Pindoles/raw/master/20191216_Multiple_testing.pdf) 
  
**[2019](https://github.com/uebvhir/Pindoles/raw/master/PINDOLES%20_UEB%20VHIR_AAFF.pdf)**  

  [28/02/2020: Busqueu la fama, i aquí és on aneu a començar a pagar: Estratègies per a la construcció de models i biomarcadors](https://github.com/uebvhir/Pindoles/raw/master/2019_02_28_Busqueu_fama_Estrategies_modelitzacio.pdf)
  
  [15/01/2020.Visualització moderna de dades](https://github.com/uebvhir/pindoles/raw/master/2020_01-Statistical_pill-Data_visualization.pdf)
  
  [16/12/2019. Ajustos per multiple testing Quan? per què? com?](https://github.com/uebvhir/Pindoles/raw/master/20191216_Multiple_testing.pdf)
  
  [21/10/2019. Sobre correlació i associació](https://github.com/uebvhir/Pindoles/raw/master/20191021_Correlation_and_Association.pdf)
  
  [27/09/2019. Odds-ratio, riscos relatius, riscos absoluts....Endreçant les idees](https://github.com/uebvhir/Pindoles/raw/master/20190927_RR_OR_Endrecant_les_idees.pdf)
  
  [28/06/2019. La crisi de la significació estadística: què diuen i què no diuen els p-valors](https://github.com/uebvhir/Pindoles/raw/master/20190628_La_crisi_de_la_significacio.pdf)
  
  [26/04/2019.Us de REDCap per a la recollida i tractament de dades en la Recerca al Campus de Vall d’Hebron](https://github.com/uebvhir/Pindoles/raw/master/Pindola_260419_Recap/Pindola_REDCap.pdf)
  
    
</div> 
  

<div class="center-title"> More Teaching </div>
  
<div class="column">

### Seminars & Special Sessions


[Sample size in animal studies - CEEA 29/11/2023](https://github.com/uebvhir/seminars/raw/master/sample_size_in_animals_CEEA.pdf)

[How to set up a container using DOCKER - HUB seminar 23/11/2023](https://github.com/uebvhir/seminars/raw/master/CONTAINER_COURSE.pdf)

 </div><


